---
title: "Import Billiken Sheets"
output: html_notebook
---

Load libraries

```{r}
library(tidyverse)
library(googlesheets4)
library(fuzzyjoin)

```

Import google sheets of Billiken League data
```{r}
(prefreeze_rosters <- read_sheet("https://docs.google.com/spreadsheets/d/1E-MsV8UEWyL3zv7ybS6a40l0sxIu7dmah2bhaBJaLNw/edit#gid=0", sheet = "PreFreezeRosters", col_types = 'ccccccc') %>% 
  filter(!is.na(player)))

(frozen_rosters <- read_sheet("https://docs.google.com/spreadsheets/d/1kMYiBTInNR3qEcyXtADD0CX7LH7dddzHF3ovbk-cWqw/edit#gid=212188698", sheet = "Frozen Rosters '24", col_types = 'cccccc'))

(draft <- read_sheet("https://docs.google.com/spreadsheets/d/1kMYiBTInNR3qEcyXtADD0CX7LH7dddzHF3ovbk-cWqw/edit#gid=212188698", sheet = "Draft '24", col_types = 'ciiiccccccccccccccc'))

(salaries <- read_sheet("https://docs.google.com/spreadsheets/d/1kMYiBTInNR3qEcyXtADD0CX7LH7dddzHF3ovbk-cWqw/edit#gid=212188698", sheet = "Salaries '24", col_types = 'ccc'))
```

Load FanGraphs Depth Charts Projections files
```{r}

hitter_projections <- read_csv("hitter_projections_2024.csv") 

pitcher_projections <- read_csv("pitcher_projections_2024.csv")

hitter_projections
pitcher_projections

```

Filter out non-player rows
```{r}
(prefreeze_rosters <- prefreeze_rosters %>% 
  filter(!is.na(player)) %>% 
  mutate(across(c("salary"), ~gsub("\\$", "", .) %>% as.numeric)))

  #filter(billikenTeam == "Free Birds")

```


Merge projections with pre-freeze rosters

```{r}
hitter_projections %>% 
#Find NL projections only
  filter(Team %in% c('ATL','LAD','SDP','ARI','NYM','PHI','MIL','STL','CHC','SFG','CIN','COL','PIT','MIA','WSN','NA')) %>%
  #left_join(prefreeze_rosters, join_by('Name'=='player')) 
  stringdist_left_join(prefreeze_rosters, by = c("Name" = "player"), max_dist = 2)

pitcher_projections %>% 
#Find NL projections only
  filter(Team %in% c('ATL','LAD','SDP','ARI','NYM','PHI','MIL','STL','CHC','SFG','CIN','COL','PIT','MIA','WSN','NA')) %>%
  #left_join(prefreeze_rosters, join_by('Name'=='player')) 
  stringdist_left_join(prefreeze_rosters, by = c("Name" = "player"), max_dist = 2)

```

Team Totals
```{r}
(hitter_team_totals <- hitter_projections %>% 
#Find NL projections only
  filter(Team %in% c('ATL','LAD','SDP','ARI','NYM','PHI','MIL','STL','CHC','SFG','CIN','COL','PIT','MIA','WSN','NA')) %>%
  stringdist_left_join(prefreeze_rosters, by = c("Name" = "player"), max_dist = 2) %>% 
  group_by(billikenTeam) %>% 
  summarize(n=n(), PA = sum(PA), AB = sum(AB), H = sum(H), HR = sum(HR), R = sum(R), RBI = sum(RBI), SB = sum(SB), AVG = sum(H)/sum(AB)))


(pitcher_team_totals <- pitcher_projections %>% 
#Find NL projections only
  filter(Team %in% c('ATL','LAD','SDP','ARI','NYM','PHI','MIL','STL','CHC','SFG','CIN','COL','PIT','MIA','WSN','NA')) %>%
  stringdist_left_join(prefreeze_rosters, by = c("Name" = "player"), max_dist = 2) %>% 
  group_by(billikenTeam) %>% 
  summarize(n=n(), W = sum(W), SV = sum(SV), IP = sum(IP), SO = sum(SO), ER = sum(ER), H = sum(H), BB = sum(BB), ERA = sum(ER)*9/sum(IP), WHIP = (sum(H)+sum(BB))/sum(IP)) )


```
Team Standings
```{r}
hitter_points <- hitter_team_totals %>% 
  filter(!is.na(billikenTeam)) %>% 
  mutate(hr = 10 - dense_rank(desc(HR)), r = 10 - dense_rank(desc(R)), rbi = 10 - dense_rank(desc(RBI)), sb = 10 - dense_rank(desc(SB)), avg = 10 - dense_rank(desc(AVG))) %>% 
  mutate(hit = hr + r + rbi + sb + avg) %>% 
  arrange(desc(hit))

pitcher_points <- pitcher_team_totals %>% 
  filter(!is.na(billikenTeam)) %>% 
  mutate(w = 10 - dense_rank(desc(W)), sv = 10 - dense_rank(desc(SV)), so = 10 - dense_rank(desc(SO)), era = 10 - dense_rank(desc(ERA)), whip = 10 - dense_rank(desc(WHIP))) %>%
  mutate(pit = w + sv + so + era + whip) %>% 
  arrange(desc(pit)) 

hitter_points %>% 
  inner_join(pitcher_points, by = join_by(billikenTeam)) %>% 
  mutate(total = hit + pit) %>% 
  select(billikenTeam, total, hr, r, rbi, sb, avg, w, sv, so, era, whip, total) %>% 
  arrange(desc(total)) 

```

Project standings variability
```{r}

hr_model <- lm(hr ~ HR, hitter_points) 
r_model <- lm(r ~ R, hitter_points) 
rbi_model <- lm(rbi ~ RBI, hitter_points) 
sb_model <- lm(sb ~ SB, hitter_points) 
avg_model <- lm(avg ~ AVG, hitter_points) 

w_model <- lm(w ~ W, pitcher_points) 
sv_model <- lm(sv ~ SV, pitcher_points) 
so_model <- lm(so ~ SO, pitcher_points) 
era_model <- lm(era ~ ERA, pitcher_points) 
whip_model <- lm(whip ~ WHIP, pitcher_points) 

hr_factor = hr_model$coefficients["HR"]
r_factor = r_model$coefficients["R"]
rbi_factor = rbi_model$coefficients["RBI"]
sb_factor = sb_model$coefficients["SB"]
avg_factor = avg_model$coefficients["AVG"]

melonheads_ab <- pull(hitter_team_totals %>% filter(billikenTeam == "Melonheads") %>% select(AB))

w_factor = w_model$coefficients["W"]
sv_factor = sv_model$coefficients["SV"]
so_factor = so_model$coefficients["SO"]
era_factor = era_model$coefficients["ERA"]
whip_factor = whip_model$coefficients["WHIP"]

```

Build list of project draft value
```{r}
#List of available players
hitter_projections %>% 
  filter(Team %in% c('ATL','LAD','SDP','ARI','NYM','PHI','MIL','STL','CHC','SFG','CIN','COL','PIT','MIA','WSN','NA')) %>%
  stringdist_left_join(prefreeze_rosters, by = c("Name" = "player"), max_dist = 2) %>% 
  filter(is.na(billikenTeam)) %>% 
  mutate(AVG = round(AVG,3)) %>% 
  mutate(avg_value = melonheads_ab)
  mutate(point_value = round(HR*hr_factor+R*r_factor+RBI*rbi_factor+SB*sb_factor,1)) %>%  #+AVG*avg_factor)
  select(Name, Team, PA, HR, R, RBI, SB, AVG, point_value, avg_value) %>% 
  arrange(desc(point_value))

```



Project/simulate draft
- Project/simulate next draft pick


Build form for draft picks with projected standings
