---
title: "In-Season Rankings 2025"
output: html_notebook
---

Pick a team to evaluate
```{r}
evaluate_team <- "Blue Socks"
other_team <- "Melonheads"
```

Update rosters with trades, omissions, etc.
```{r}
trade_players <- data.frame(player_name = character(), 
                        new_team = character(),
                        stringsAsFactors = FALSE)

trade_players[1,] <- c("Nolan Arenado","Blue Socks")
# trade_players[2,] <- c("Masyn Winn","Westside Marauders")
# trade_players[3,] <- c("Lars Nootbaar","Free Birds")
# trade_players[4,] <- c("Brendan Donovan","National Pastime")
# trade_players[5,] <- c("Jeff McNeil","Westside Marauders")
# trade_players[6,] <- c("Ivan Herrera","National Pastime")
# trade_players[7,] <- c("Willson Contreras","Louisville Sluggers")
# trade_players[8,] <- c("Victor Scott II","Louisville Sluggers")
# trade_players[9,] <- c("Nolan Gorman","Hoosiers")
# trade_players[10,] <- c("Alex Burleson","National Pastime")
# trade_players[11,] <- c("Pedro Pages","Big Red Machine")
# trade_players[12,] <- c("Jordan Walker","Hoosiers")
# trade_players[13,] <- c("Sonny Gray","Erie Lakers")
# trade_players[14,] <- c("Ryan Helsley","Hoosiers")


#trade_players[13,] <- c("Bryce Harper","Blue Socks")
#trade_players[14,] <- c("Jeimer Candelario","Free At Last")


trade_players
#hitter_proj_ros_export
```


Load libraries

```{r eval=TRUE, include=TRUE}
library(tidyverse)
library(googlesheets4)
library(fuzzyjoin)

```

Import google sheets of Billiken League data
```{r echo=TRUE}

#Pull rosters data
rosters_import <- read_sheet("https://docs.google.com/spreadsheets/d/1nfL9yd09BNp0DWU7y5P36P_EMj_I6Aaf40K_k-9-IpU/edit?gid=724458944#gid=724458944", sheet = "Rosters", col_types = 'cccccc') %>% 
  filter(!is.na(Player))

#If you created a new google sheet, don't forget to change sharing permissions to "anyone with the link can edit" or you will get OAuth errors
season_stats <- read_sheet("https://docs.google.com/spreadsheets/d/1nfL9yd09BNp0DWU7y5P36P_EMj_I6Aaf40K_k-9-IpU/edit?gid=724458944#gid=724458944", sheet = "SeasonStats", col_types = 'cciiiidiiiddii') 

```

Load FanGraphs Depth Charts Projections files
```{r eval=TRUE, include=TRUE}
hitter_projections_import <- read_csv("hitter_projections_ros.csv") %>% 
  mutate(Name = stringi::stri_trans_general(Name, "Latin-ASCII"))
pitcher_projections_import <- read_csv("pitcher_projections_ros.csv") %>% 
  mutate(Name = stringi::stri_trans_general(Name, "Latin-ASCII"))

hitter_projections_import
pitcher_projections_import

```

Import rosters 
```{r}
rosters <- rosters_import %>% 
  rename(billikenTeam = BillikenTeam, player = Player) %>% 
  mutate(billikenTeam = str_to_title(billikenTeam)) %>% 
  select(player, billikenTeam)

#rosters %>% filter(billikenTeam == "Blue Socks")

rosters
```


Merge projections with rosters and filter on NL teams only
```{r}
hitter_projections <- hitter_projections_import %>% 
#Find NL projections only
  filter(Team %in% c('ATL','LAD','SDP','ARI','NYM','PHI','MIL','STL','CHC','SFG','CIN','COL','PIT','MIA','WSN','NA')) %>%
  stringdist_left_join(rosters, by = c("Name" = "player"), max_dist = 2)

pitcher_projections <- pitcher_projections_import %>% 
#Find NL projections only
  filter(Team %in% c('ATL','LAD','SDP','ARI','NYM','PHI','MIL','STL','CHC','SFG','CIN','COL','PIT','MIA','WSN','NA')) %>%
  stringdist_left_join(rosters, by = c("Name" = "player"), max_dist = 2)


```

Update traded players
```{r}
#rosters %>% 
#  filter(player == "Bryce Harper")
  

for (i in 1:nrow(trade_players))
{
    traded_player_name <- trade_players[i,]$player_name
    traded_new_team <- trade_players[i,]$new_team
    
    hitter_projections <- hitter_projections %>% 
      mutate(billikenTeam = ifelse(Name == traded_player_name, traded_new_team, billikenTeam))
    
    pitcher_projections <- pitcher_projections %>% 
      mutate(billikenTeam = ifelse(Name == traded_player_name, traded_new_team, billikenTeam))
}

#rosters %>% 
#  filter(player == "Bryce Harper")
 

```



```{r}
hitter_proj_ros_export <- hitter_projections %>% 
  select(Name, billikenTeam, Team, G, PA, AB, H, HR, R, RBI, SB, AVG)

hitter_proj_ros_export
```



Team Totals
```{r}
(hitter_team_totals <- hitter_projections %>% 
#Find NL projections only
  #filter(Team %in% c('ATL','LAD','SDP','ARI','NYM','PHI','MIL','STL','CHC','SFG','CIN','COL','PIT','MIA','WSN','NA')) %>%
  #stringdist_left_join(prefreeze_rosters, by = c("Name" = "player"), max_dist = 2) %>% 
  group_by(billikenTeam) %>% 
  summarize(n=n(), PA = sum(PA), AB = sum(AB), H = sum(H), HR = sum(HR), R = sum(R), RBI = sum(RBI), SB = sum(SB), AVG = sum(H)/sum(AB)))


(pitcher_team_totals <- pitcher_projections %>% 
#Find NL projections only
  #filter(Team %in% c('ATL','LAD','SDP','ARI','NYM','PHI','MIL','STL','CHC','SFG','CIN','COL','PIT','MIA','WSN','NA')) %>%
  #stringdist_left_join(prefreeze_rosters, by = c("Name" = "player"), max_dist = 2) %>% 
  group_by(billikenTeam) %>% 
  summarize(n=n(), W = sum(W), SV = sum(SV), IP = sum(IP), SO = sum(SO), ER = sum(ER), H = sum(H), BB = sum(BB), ERA = sum(ER)*9/sum(IP), WHIP = (sum(H)+sum(BB))/sum(IP)) )


```

```{r}
AB_R_RBI_ratio <- pull(hitter_projections %>% 
  filter(AB > 350) %>% 
  summarize(R = sum(R), RBI = sum(RBI), AB = sum(AB)) %>% 
  mutate(AB_R_RBI_ratio = AB/(R+RBI)) %>% 
  select(AB_R_RBI_ratio))

season_stats_clean <- season_stats %>% 
  rename(billikenTeam = Team, SO = K) %>% 
  mutate(AB = (R+RBI)*AB_R_RBI_ratio, H = AVG*(R+RBI)*AB_R_RBI_ratio, H_BB = IP*WHIP, ER = IP*ERA/9) %>% 
  select(billikenTeam, AB, H, HR, R, RBI, SB, IP, W, SV, SO, H_BB, ER)

#rows_update(season_stats_clean, tibble(billikenTeam = "Free at Last", billikenTeam = "Free At Last")) 

season_stats_clean <- season_stats_clean %>% 
  mutate(billikenTeam = ifelse(billikenTeam == "Free at Last", "Free At Last", billikenTeam))

hitter_team_clean <- hitter_team_totals %>% 
  filter(!is.na(billikenTeam)) %>% 
  mutate(IP = 0, W = 0, SV = 0, SO = 0, H_BB = 0, ER = 0) %>% 
select(billikenTeam, AB, H, HR, R, RBI, SB, IP, W, SV, SO, H_BB, ER)

pitcher_team_clean <- pitcher_team_totals %>% 
  filter(!is.na(billikenTeam)) %>% 
  mutate(H_BB = H + BB) %>% 
  mutate(AB = 0, H = 0, HR = 0, R = 0, RBI = 0, SB = 0) %>% 
  select(billikenTeam, AB, H, HR, R, RBI, SB, IP, W, SV, SO, H_BB, ER)

projected_final_team_stats <- rbind(season_stats_clean, hitter_team_clean, pitcher_team_clean) %>% 
  group_by(billikenTeam) %>% 
  summarize(AB = sum(AB), H = sum(H), HR = sum(HR), R = sum(R), RBI = sum(RBI), SB = sum(SB), 
            IP = sum(IP), W = sum(W), SV = sum(SV), SO = sum(SO), H_BB = sum(H_BB), ER = sum(ER)) %>% 
  mutate(AVG = H/AB, WHIP = H_BB/IP, ERA = ER/IP*9) 

```


Team Standings
```{r}
#Rank Team Totals
n_teams <- pull(count(projected_final_team_stats %>% filter(!is.na(billikenTeam)) %>% distinct(billikenTeam)))

team_points <- projected_final_team_stats %>% 
  filter(!is.na(billikenTeam)) %>% 
  mutate(hr = n_teams+1 - dense_rank(desc(HR)), r = n_teams+1 - dense_rank(desc(R)), rbi = n_teams+1 - dense_rank(desc(RBI)), sb = n_teams+1 - dense_rank(desc(SB)), avg = n_teams+1 - dense_rank(desc(AVG))) %>% 
  mutate(hr_pct = (hr-1)/(n_teams-1), r_pct = (r-1)/(n_teams-1), rbi_pct = (rbi-1)/(n_teams-1), sb_pct = (sb-1)/(n_teams-1), avg_pct = (avg-1)/(n_teams-1)) %>% 
  mutate(w = n_teams+1 - dense_rank(desc(W)), sv = n_teams+1 - dense_rank(desc(SV)), so = n_teams+1 - dense_rank(desc(SO)), era = n_teams+1 - dense_rank(ERA), whip = n_teams+1 - dense_rank(WHIP)) %>%
  mutate(w_pct = (w-1)/(n_teams-1), sv_pct = (sv-1)/(n_teams-1), so_pct = (so-1)/(n_teams-1), era_pct = (era-1)/(n_teams-1), whip_pct = (whip-1)/(n_teams-1)) %>%
  mutate(points = hr + r + rbi + sb + avg + w + sv + so + era + whip) %>% 
  arrange(desc(points))

```

Project category variability demo
```{r}
ggplot(team_points, aes(AVG, avg_pct)) +
  geom_point() +
  stat_smooth(method="glm", method.args = list(family=binomial))

ggplot(team_points, aes(ERA, era_pct)) +
  geom_point() +
  stat_smooth(method="glm", method.args = list(family=binomial))

```

Fit logistic regression curves
```{r}
hr_model_glm <- glm(hr_pct ~ HR, data = team_points, family = "binomial")
team_points$hr_pts_pred = predict(hr_model_glm, team_points, type="response")*9+1

r_model_glm <- glm(r_pct ~ R, data = team_points, family = "binomial")
team_points$r_pts_pred = predict(r_model_glm, team_points, type="response")*9+1

rbi_model_glm <- glm(rbi_pct ~ RBI, data = team_points, family = "binomial")
team_points$rbi_pts_pred = predict(rbi_model_glm, team_points, type="response")*9+1

sb_model_glm <- glm(sb_pct ~ SB, data = team_points, family = "binomial")
team_points$sb_pts_pred = predict(sb_model_glm, team_points, type="response")*9+1

avg_model_glm <- glm(avg_pct ~ AVG, data = team_points, family = "binomial")
team_points$avg_pts_pred = predict(hr_model_glm, team_points, type="response")*9+1

w_model_glm <- glm(w_pct ~ W, data = team_points, family = "binomial")
team_points$w_pts_pred = predict(w_model_glm, team_points, type="response")*9+1

sv_model_glm <- glm(sv_pct ~ SV, data = team_points, family = "binomial")
team_points$sv_pts_pred = predict(sv_model_glm, team_points, type="response")*9+1

so_model_glm <- glm(so_pct ~ SO, data = team_points, family = "binomial")
team_points$so_pts_pred = predict(so_model_glm, team_points, type="response")*9+1

era_model_glm <- glm(era_pct ~ ERA, data = team_points, family = "binomial")
team_points$era_pts_pred = predict(era_model_glm, team_points, type="response")*9+1

whip_model_glm <- glm(whip_pct ~ WHIP, data = team_points, family = "binomial")
team_points$whip_pts_pred = predict(whip_model_glm, team_points, type="response")*9+1

(team_points <- team_points %>% 
  mutate(team_points_pred = hr_pts_pred + r_pts_pred + rbi_pts_pred + sb_pts_pred + avg_pts_pred + 
           w_pts_pred + sv_pts_pred + so_pts_pred + era_pts_pred + whip_pts_pred) %>% 
    arrange(billikenTeam) )


```


```{r}
team_points %>% 
  select(billikenTeam, points, team_points_pred, hr, r, rbi, sb, avg, w, sv, so, era, whip, points) %>% 
  arrange(desc(team_points_pred)) 

write_csv(team_points, "projected_final_standings.csv")

```

Combine Hitter and Pitcher Projections
```{r}
projected_players <- bind_rows(hitter_projections, pitcher_projections) %>% 
  #stringdist_left_join(positions, by = c("Name" = "player"), max_dist = 2) %>% 
  #stringdist_left_join(salaries, by = c("Name" = "Player"), max_dist = 2) %>% 
  #mutate(salary = case_when(!is.na(billikenTeam) ~ salary, TRUE ~ new_salary)) %>% 
  #filter(is.na(Owner) & !is.na(billikenTeam)) %>% 
  mutate(AVG = round(AVG,3), ERA = round(ERA,2), WHIP = round(WHIP,2), SO = case_when(IP == 0 ~ NA, IP > 0 ~ SO)) %>%  
  mutate(HR = case_when(PA == 0 ~ NA, PA > 0 ~ HR), R = case_when(PA == 0 ~ NA, PA > 0 ~ R), AVG = case_when(PA == 0 ~ NA, PA > 0 ~ AVG)) %>% 
  mutate(WH = WHIP*IP) %>% 
  mutate(H = ifelse(PA>0,H,0)) %>% 
  select(Name, billikenTeam, #contract, salary, 
         Team, PA, AB, H, HR, R, RBI, SB, AVG, IP, WH, ER, W, SV, SO, ERA, WHIP#, point_value, #p_c, p_1b, p_2b, p_3b, p_ss, p_of, p_ci, p_mi, p_dh, p_util
         ) #%>% 
  #arrange(desc(point_value)) 

projected_players

```

Loop through every projected player
- If on evaluate_team, switch them to other_team
- If not on evaluate_team, switch to evaluate_team
Rerun standings
Record difference in evaluate_team's standings
Move on to next player


```{r echo=TRUE}
projected_players_blue_socks <- projected_players %>% 
  filter(billikenTeam == "Blue Socks")

projected_players_blue_socks$points_impact <- 0
projected_players_blue_socks$points_pred_impact <- 0

for (i in 1:nrow(projected_players_blue_socks)
     )
  {
  
#i <- 1

#i <- (1:nrow(projected_players))[projected_players[,"Name"] == "Alex Call"]
  
  projected_players_sim <- projected_players_blue_socks
  
  player_name <- projected_players_sim[i,]$Name
  
  player_team <- coalesce(projected_players_sim[i,]$billikenTeam,"None")
    
  projected_players_sim[i,]$billikenTeam <- ifelse(player_team == evaluate_team, other_team, evaluate_team)
  
  #re-add team stats with new rosters
  projected_players_sim <- projected_players_sim %>% 
    replace_na(list(PA = 0, AB = 0, H = 0, HR = 0, R = 0, RBI = 0, SB = 0, IP = 0, WH = 0, W = 0, SV = 0, SO = 0, ER = 0))
  
  projected_team_totals_sim <- projected_players_sim %>% 
    group_by(billikenTeam) %>% 
    filter(!is.na(billikenTeam)) %>% 
    mutate(H_BB = WH) %>% 
    summarize(n=n(), PA = sum(PA), AB = sum(AB), H = sum(H), HR = sum(HR), R = sum(R), RBI = sum(RBI), SB = sum(SB), 
              AVG = sum(H)/sum(AB), W = sum(W), SV = sum(SV), IP = sum(IP), SO = sum(SO), ER = sum(ER), H_BB = sum(H_BB),
              ERA = sum(ER)*9/sum(IP), WHIP = (sum(H_BB)/sum(IP))) %>% 
    select(billikenTeam, AB, H, HR, R, RBI, SB, IP, W, SV, SO, H_BB, ER)
  
  projected_final_team_stats_sim <- rbind(season_stats_clean, projected_team_totals_sim) %>% 
    group_by(billikenTeam) %>% 
    summarize(AB = sum(AB), H = sum(H), HR = sum(HR), R = sum(R), RBI = sum(RBI), SB = sum(SB), 
              IP = sum(IP), W = sum(W), SV = sum(SV), SO = sum(SO), H_BB = sum(H_BB), ER = sum(ER)) %>% 
    mutate(AVG = H/AB, WHIP = H_BB/IP, ERA = ER/IP*9) 

  #calculate new team standings
  
  team_points_sim <- projected_final_team_stats_sim %>% 
    filter(!is.na(billikenTeam)) %>% 
    mutate(hr = n_teams+1 - dense_rank(desc(HR)), r = n_teams+1 - dense_rank(desc(R)), 
           rbi = n_teams+1 - dense_rank(desc(RBI)), sb = n_teams+1 - dense_rank(desc(SB)), 
           avg = n_teams+1 - dense_rank(desc(AVG))) %>% 
    mutate(hr_pct = (hr-1)/(n_teams-1), r_pct = (r-1)/(n_teams-1), 
           rbi_pct = (rbi-1)/(n_teams-1), sb_pct = (sb-1)/(n_teams-1), 
           avg_pct = (avg-1)/(n_teams-1)) %>% 
    mutate(w = n_teams+1 - dense_rank(desc(W)), sv = n_teams+1 - dense_rank(desc(SV)), 
           so = n_teams+1 - dense_rank(desc(SO)), era = n_teams+1 - dense_rank(ERA), 
           whip = n_teams+1 - dense_rank(WHIP)) %>%
    mutate(w_pct = (w-1)/(n_teams-1), sv_pct = (sv-1)/(n_teams-1), 
           so_pct = (so-1)/(n_teams-1), era_pct = (era-1)/(n_teams-1), 
           whip_pct = (whip-1)/(n_teams-1)) %>%
    mutate(points = hr + r + rbi + sb + avg + w + sv + so + era + whip) %>% 
    arrange(desc(points))
    
  #calculate predicted points
  
  hr_model_glm_sim <- suppressWarnings(glm(hr_pct ~ HR, data = team_points_sim, family = "binomial"))
  team_points_sim$hr_pts_pred = predict(hr_model_glm_sim, team_points_sim, type="response")*9+1
  
  r_model_glm_sim <- suppressWarnings(glm(r_pct ~ R, data = team_points_sim, family = "binomial"))
  team_points_sim$r_pts_pred = predict(r_model_glm_sim, team_points_sim, type="response")*9+1
  
  rbi_model_glm_sim <- suppressWarnings(glm(rbi_pct ~ RBI, data = team_points_sim, family = "binomial"))
  team_points_sim$rbi_pts_pred = predict(rbi_model_glm_sim, team_points_sim, type="response")*9+1
  
  sb_model_glm_sim <- suppressWarnings(glm(sb_pct ~ SB, data = team_points_sim, family = "binomial"))
  team_points_sim$sb_pts_pred = predict(sb_model_glm_sim, team_points_sim, type="response")*9+1
  
  avg_model_glm_sim <- suppressWarnings(glm(avg_pct ~ AVG, data = team_points_sim, family = "binomial"))
  team_points_sim$avg_pts_pred = predict(hr_model_glm_sim, team_points_sim, type="response")*9+1
  
  w_model_glm_sim <- suppressWarnings(glm(w_pct ~ W, data = team_points_sim, family = "binomial"))
  team_points_sim$w_pts_pred = predict(w_model_glm_sim, team_points_sim, type="response")*9+1
  
  sv_model_glm_sim <- suppressWarnings(glm(sv_pct ~ SV, data = team_points_sim, family = "binomial"))
  team_points_sim$sv_pts_pred = predict(sv_model_glm_sim, team_points_sim, type="response")*9+1
  
  so_model_glm_sim <- suppressWarnings(glm(so_pct ~ SO, data = team_points_sim, family = "binomial"))
  team_points_sim$so_pts_pred = predict(so_model_glm_sim, team_points_sim, type="response")*9+1
  
  era_model_glm_sim <- suppressWarnings(glm(era_pct ~ ERA, data = team_points_sim, family = "binomial"))
  team_points_sim$era_pts_pred = predict(era_model_glm_sim, team_points_sim, type="response")*9+1
  
  whip_model_glm_sim <- suppressWarnings(glm(whip_pct ~ WHIP, data = team_points_sim, family = "binomial"))
  team_points_sim$whip_pts_pred = predict(whip_model_glm_sim, team_points_sim, type="response")*9+1
  
  team_points_sim <- team_points_sim %>% 
    mutate(team_points_pred = hr_pts_pred + r_pts_pred + rbi_pts_pred + sb_pts_pred + avg_pts_pred + 
             w_pts_pred + sv_pts_pred + so_pts_pred + era_pts_pred + whip_pts_pred) %>% 
      arrange(desc(team_points_pred))
  
  #compare before and after stats from team_points and team_points_sim
  
  before_points <- pull(team_points %>% filter(billikenTeam == evaluate_team) %>% select(points)) 
  before_points_pred <- pull(team_points %>% filter(billikenTeam == evaluate_team) %>% select(team_points_pred)) 
  
  after_points <- pull(team_points_sim %>% filter(billikenTeam == evaluate_team) %>% select(points))
  after_points_pred <- pull(team_points_sim %>% filter(billikenTeam == evaluate_team) %>% select(team_points_pred))
  
  #record delta in player projections row
  
  projected_players_blue_socks[i,]$points_impact <- abs(after_points - before_points)
  projected_players_blue_socks[i,]$points_pred_impact <- abs(after_points_pred - before_points_pred)
  
  print(player_name)
  #team_points
  #team_points_sim
  
}

projected_players_blue_socks <- projected_players_blue_socks %>% 
  arrange(desc(abs(points_pred_impact)))

projected_players_blue_socks


```



```{r}
projected_players$points_impact <- 0
projected_players$points_pred_impact <- 0

for (i in 1:3 #nrow(projected_players)
     )
  {

#i <- 1

#i <- (1:nrow(projected_players))[projected_players[,"Name"] == "Alex Call"]
  
  projected_players_sim <- projected_players
  
  player_name <- projected_players_sim[i,]$Name
  
  player_team <- coalesce(projected_players_sim[i,]$billikenTeam,"None")
    
  projected_players_sim[i,]$billikenTeam <- ifelse(player_team == evaluate_team, other_team, evaluate_team)
  
  #re-add team stats with new rosters
  projected_players_sim <- projected_players_sim %>% 
    replace_na(list(PA = 0, AB = 0, H = 0, HR = 0, R = 0, RBI = 0, SB = 0, IP = 0, WH = 0, W = 0, SV = 0, SO = 0, ER = 0))
  
  projected_team_totals_sim <- projected_players_sim %>% 
    group_by(billikenTeam) %>% 
    filter(!is.na(billikenTeam)) %>% 
    mutate(H_BB = WH) %>% 
    summarize(n=n(), PA = sum(PA), AB = sum(AB), H = sum(H), HR = sum(HR), R = sum(R), RBI = sum(RBI), SB = sum(SB), 
              AVG = sum(H)/sum(AB), W = sum(W), SV = sum(SV), IP = sum(IP), SO = sum(SO), ER = sum(ER), H_BB = sum(H_BB),
              ERA = sum(ER)*9/sum(IP), WHIP = (sum(H_BB)/sum(IP))) %>% 
    select(billikenTeam, AB, H, HR, R, RBI, SB, IP, W, SV, SO, H_BB, ER)
  
  projected_final_team_stats_sim <- rbind(season_stats_clean, projected_team_totals_sim) %>% 
    group_by(billikenTeam) %>% 
    summarize(AB = sum(AB), H = sum(H), HR = sum(HR), R = sum(R), RBI = sum(RBI), SB = sum(SB), 
              IP = sum(IP), W = sum(W), SV = sum(SV), SO = sum(SO), H_BB = sum(H_BB), ER = sum(ER)) %>% 
    mutate(AVG = H/AB, WHIP = H_BB/IP, ERA = ER/IP*9) 

  #calculate new team standings
  
  team_points_sim <- projected_final_team_stats_sim %>% 
    filter(!is.na(billikenTeam)) %>% 
    mutate(hr = n_teams+1 - dense_rank(desc(HR)), r = n_teams+1 - dense_rank(desc(R)), 
           rbi = n_teams+1 - dense_rank(desc(RBI)), sb = n_teams+1 - dense_rank(desc(SB)), 
           avg = n_teams+1 - dense_rank(desc(AVG))) %>% 
    mutate(hr_pct = (hr-1)/(n_teams-1), r_pct = (r-1)/(n_teams-1), 
           rbi_pct = (rbi-1)/(n_teams-1), sb_pct = (sb-1)/(n_teams-1), 
           avg_pct = (avg-1)/(n_teams-1)) %>% 
    mutate(w = n_teams+1 - dense_rank(desc(W)), sv = n_teams+1 - dense_rank(desc(SV)), 
           so = n_teams+1 - dense_rank(desc(SO)), era = n_teams+1 - dense_rank(ERA), 
           whip = n_teams+1 - dense_rank(WHIP)) %>%
    mutate(w_pct = (w-1)/(n_teams-1), sv_pct = (sv-1)/(n_teams-1), 
           so_pct = (so-1)/(n_teams-1), era_pct = (era-1)/(n_teams-1), 
           whip_pct = (whip-1)/(n_teams-1)) %>%
    mutate(points = hr + r + rbi + sb + avg + w + sv + so + era + whip) %>% 
    arrange(desc(points))
    
  #calculate predicted points
  
  hr_model_glm_sim <- suppressWarnings(glm(hr_pct ~ HR, data = team_points_sim, family = "binomial"))
  team_points_sim$hr_pts_pred = predict(hr_model_glm_sim, team_points_sim, type="response")*9+1
  
  r_model_glm_sim <- suppressWarnings(glm(r_pct ~ R, data = team_points_sim, family = "binomial"))
  team_points_sim$r_pts_pred = predict(r_model_glm_sim, team_points_sim, type="response")*9+1
  
  rbi_model_glm_sim <- suppressWarnings(glm(rbi_pct ~ RBI, data = team_points_sim, family = "binomial"))
  team_points_sim$rbi_pts_pred = predict(rbi_model_glm_sim, team_points_sim, type="response")*9+1
  
  sb_model_glm_sim <- suppressWarnings(glm(sb_pct ~ SB, data = team_points_sim, family = "binomial"))
  team_points_sim$sb_pts_pred = predict(sb_model_glm_sim, team_points_sim, type="response")*9+1
  
  avg_model_glm_sim <- suppressWarnings(glm(avg_pct ~ AVG, data = team_points_sim, family = "binomial"))
  team_points_sim$avg_pts_pred = predict(hr_model_glm_sim, team_points_sim, type="response")*9+1
  
  w_model_glm_sim <- suppressWarnings(glm(w_pct ~ W, data = team_points_sim, family = "binomial"))
  team_points_sim$w_pts_pred = predict(w_model_glm_sim, team_points_sim, type="response")*9+1
  
  sv_model_glm_sim <- suppressWarnings(glm(sv_pct ~ SV, data = team_points_sim, family = "binomial"))
  team_points_sim$sv_pts_pred = predict(sv_model_glm_sim, team_points_sim, type="response")*9+1
  
  so_model_glm_sim <- suppressWarnings(glm(so_pct ~ SO, data = team_points_sim, family = "binomial"))
  team_points_sim$so_pts_pred = predict(so_model_glm_sim, team_points_sim, type="response")*9+1
  
  era_model_glm_sim <- suppressWarnings(glm(era_pct ~ ERA, data = team_points_sim, family = "binomial"))
  team_points_sim$era_pts_pred = predict(era_model_glm_sim, team_points_sim, type="response")*9+1
  
  whip_model_glm_sim <- suppressWarnings(glm(whip_pct ~ WHIP, data = team_points_sim, family = "binomial"))
  team_points_sim$whip_pts_pred = predict(whip_model_glm_sim, team_points_sim, type="response")*9+1
  
  team_points_sim <- team_points_sim %>% 
    mutate(team_points_pred = hr_pts_pred + r_pts_pred + rbi_pts_pred + sb_pts_pred + avg_pts_pred + 
             w_pts_pred + sv_pts_pred + so_pts_pred + era_pts_pred + whip_pts_pred) %>% 
      arrange(billikenTeam)
  
  #compare before and after stats from team_points and team_points_sim
  
  before_points <- pull(team_points %>% filter(billikenTeam == evaluate_team) %>% select(points)) 
  before_points_pred <- pull(team_points %>% filter(billikenTeam == evaluate_team) %>% select(team_points_pred)) 
  
  after_points <- pull(team_points_sim %>% filter(billikenTeam == evaluate_team) %>% select(points))
  after_points_pred <- pull(team_points_sim %>% filter(billikenTeam == evaluate_team) %>% select(team_points_pred))
  
  #record delta in player projections row
  
  projected_players[i,]$points_impact <- abs(after_points - before_points)
  projected_players[i,]$points_pred_impact <- abs(after_points_pred - before_points_pred)
  
  print(player_name)
  print(team_points)
  print(team_points_sim)
  
}

projected_players <- projected_players %>% 
  arrange(desc(abs(points_pred_impact)))

projected_players %>% 
  filter(billikenTeam == "Blue Socks")

write_csv(projected_players, "proj_impact.csv")

```






