---
title: "Draft Simulation 2025"
output: html_notebook
---

Must be run after Draft_Rankings_2025


Roster positions

```{r}
# Example input lists
positions_list <- c("p", "p", "p", "p", "p", "p", "p", "p", "p", "c", "c", "1b", "2b", "3b", "ss", "of", "of", "of", "of", "of", "mi", "ci", "dh", "util", "minors", "minors", "minors")
team_names <- c("Blue Socks", "Free At Last", "Melonheads", "Free Birds", "Westside Marauders", "Louisville Sluggers", "Hoosiers", "Erie Lakers", "National Pastime", "Big Red Machine")

# Create a tibble with one row for each combination of team name and position
team_position_tibble <- expand_grid(team = team_names, pos = positions_list)

team_position_tibble <- team_position_tibble %>% 
  mutate(p_c = case_when(pos=="c" ~ 1, .default = 0)) %>% 
  mutate(p_1b = case_when(pos=="1b" ~ 1, .default = 0)) %>% 
  mutate(p_2b = case_when(pos=="2b" ~ 1, .default = 0)) %>% 
  mutate(p_3b = case_when(pos=="3b" ~ 1, .default = 0)) %>% 
  mutate(p_ss = case_when(pos=="ss" ~ 1, .default = 0)) %>% 
  mutate(p_of = case_when(pos=="of" ~ 1, .default = 0)) %>% 
  mutate(p_ci = case_when(pos=="ci" ~ 1, .default = 0)) %>% 
  mutate(p_mi = case_when(pos=="mi" ~ 1, .default = 0)) %>% 
  mutate(p_dh = case_when(pos=="dh" ~ 1, .default = 0)) %>% 
  mutate(p_util = case_when(pos=="util" ~ 1, .default = 0)) %>% 
  mutate(p_p = case_when(pos=="p" ~ 1, .default = 0)) %>% 
  mutate(player = NA) %>% 
  mutate(row = row_number()) %>% 
  relocate(player, .after = pos)

```

Configure rosters
```{r}
rostered_players <- par %>% 
  filter(!is.na(billikenTeam)) %>% 
  #mutate(p_util = case_when(PA > 0 ~ 1, .default = 0)) %>% 
  mutate(p_p = case_when(IP > 0 ~ 1, .default = 0)) 

#order by single position players first

rostered_players_pos_pivot <- 
  rostered_players %>%
    pivot_longer(
      cols = starts_with("p_"),
      names_to = "pos",
      names_prefix = "p_",
      values_to = "eligible",
      values_drop_na = TRUE
    ) %>% 
    filter(eligible == 1) %>% 
    filter(is.na(IP) | pos == "p")
```


fill rosters with keepers and drafted players
```{r}
f_fill_keepers <- function() {
  
  for (i in 1:nrow(rostered_players)) {
  #for (i in 1:120) {
  
  #i <- 121
  print(i)
  
  #Name
  v_player <- rostered_players$Name[i]
  #v_player <- "Isiah Kiner-Falefa"
  #team
  v_team <- rostered_players$billikenTeam[i]
  #v_team <- "Free Birds"
  
  print(v_player)
  print(v_team)
  
  #check open positions on team
  open_positions <<- team_position_tibble %>% 
    filter(team == v_team) %>% 
    #filter(team == "Blue Socks") %>% 
    filter(is.na(player))  
  
  #assign position
  v_row <- pull(rostered_players_pos_pivot %>% 
                  filter(Name == v_player) %>% #positions this player can play
                  inner_join(replacement_level, join_by(pos)) %>% 
                  inner_join(open_positions, join_by(pos)) %>% 
                  arrange(repl_level) %>% 
                  slice(1) %>% 
                  select(row)
                )

  #could add logic to put a player on the bench if doesn't fit in current configuration
  
  v_row <- ifelse(length(v_row)==0,0,v_row)
  
  print(v_row)
  
  #write player into position
  team_position_tibble <<- team_position_tibble %>% 
    mutate(player = ifelse(row == v_row,v_player,player))
    }
  
team_position_tibble %>% 
  arrange(player)

}
  
```

Set up n simulations
```{r}



```


Start a single simulation of the draft

Set up simulated rosters, including latest real world picks
```{r}
simulated_rosters <- par


```

Start a single simulated pick

create available rosters
```{r}
f_reset_eligible_players <- function() {
  
  #create available players list
  available_players <<- simulated_rosters %>% 
    filter(is.na(billikenTeam)) %>% 
    mutate(p_p = case_when(IP > 0 ~ 1, .default = 0))
    
  #pivot to one row per available position
  available_players_pos_pivot <<- available_players %>%
    pivot_longer(
      cols = starts_with("p_"),
      names_to = "pos",
      names_prefix = "p_",
      values_to = "eligible",
      values_drop_na = TRUE
    ) %>% 
    filter(eligible == 1) %>% 
    filter(is.na(IP) | pos == "p")
  
}
  
```


next eligible players for remaining roster spots
```{r}
f_make_pick <- function(v_drafting_team) {


  #pick a team
  #v_drafting_team <- "Blue Socks"

  #check if roster is full
    #if so, end

  #determine open roster spots
  open_positions <<- team_position_tibble %>% 
    filter(team == v_drafting_team) %>% 
    filter(is.na(player))  

  #distinct eligible players to be selected
  eligible_players <<- available_players_pos_pivot %>% 
    inner_join(open_positions, join_by(pos)) %>% 
    arrange(desc(ev)) %>% 
    distinct(Name, .keep_all = TRUE) 
  
  #check salary cap for eligibility

  #add some randomness to the draft
  eligible_players$rand <- rnorm(nrow(eligible_players), mean = 0, sd = 2)
  
  #add smarter picks for Blue Socks, other teams? 
  
  #make pick
  v_player <- pull(eligible_players %>% 
    mutate(rand_ev = ev + rand) %>% 
    arrange(desc(rand_ev)) %>% 
    slice(1) %>% 
    select(Name))
  
  #assign position to selected player
  v_row <- pull(available_players_pos_pivot %>% 
                  filter(Name == v_player) %>% #positions this player can play
                  inner_join(replacement_level, join_by(pos)) %>% 
                  inner_join(open_positions, join_by(pos)) %>% 
                  arrange(repl_level) %>% 
                  slice(1) %>% 
                  select(row)
                )
  
  print(v_row)
  
  #write player into position
  team_position_tibble <<- 
    team_position_tibble %>% 
      mutate(player = ifelse(row == v_row,v_player,player))
  
#updated simulated rosters
  simulated_rosters <<- simulated_rosters %>% 
      mutate(billikenTeam = ifelse(Name == v_player,v_drafting_team,billikenTeam))
}

#simulated_rosters
#team_position_tibble
  
```


```{r}
draft_order <- draft %>%
  rename(player = "Player...1", billikenTeam = Team, salary = Salary) %>% 
  mutate(contract = 1, salary = salary %>% as.numeric) %>% 
  filter(is.na(player)) %>% 
  select(player, Round, Pick, billikenTeam, Owner)
```

Function to identify the team that's on the clock for the next pick
```{r}
f_team_on_clock <- function() {
    
  pull(draft_order %>% 
         arrange(Round, Pick) %>% 
         slice(1) %>% 
         select(billikenTeam)
         )
  }

```

Make 1 pick
```{r}
f_make_next_pick <- function() {
  
  f_reset_eligible_players()

  f_make_pick(f_team_on_clock())
  
}
```

Test making one pick
```{r}

f_fill_keepers()

test_team <- f_team_on_clock()

simulated_rosters %>% 
  filter(billikenTeam == test_team) %>% 
  arrange(desc(contract))

team_position_tibble %>% 
  filter(team == test_team)

f_make_next_pick()
  
simulated_rosters %>% 
  filter(billikenTeam == test_team) %>% 
  arrange(desc(contract))

team_position_tibble %>% 
  filter(team == test_team)


```


Run 1 simulated draft
```{r}


my_function <- function(fname, lname) {
  paste(fname, lname)
  
  f_fill_keepers
  
}

my_function("Peter", "Griffin")


```

