---
title: "Draft Simulation 2025"
output: html_notebook
---

Must be run after Draft_Rankings_2025


Function to create empty rosters
```{r}

f_create_empty_rosters <- function() {
  # Example input lists
  positions_list <- c("p", "p", "p", "p", "p", "p", "p", "p", "p", "c", "c", "1b", "2b", "3b", "ss", "of", "of", "of", "of", "of", "mi", "ci", "dh", "util", "minors", "minors", "minors")
  team_names <- c("Blue Socks", "Free At Last", "Melonheads", "Free Birds", "Westside Marauders", "Louisville Sluggers", "Hoosiers", "Erie Lakers", "National Pastime", "Big Red Machine")
  
  # Create a tibble with one row for each combination of team name and position
  team_position_tibble <<- expand_grid(team = team_names, pos = positions_list)
  
  team_position_tibble <<- team_position_tibble %>% 
    mutate(p_c = case_when(pos=="c" ~ 1, .default = 0)) %>% 
    mutate(p_1b = case_when(pos=="1b" ~ 1, .default = 0)) %>% 
    mutate(p_2b = case_when(pos=="2b" ~ 1, .default = 0)) %>% 
    mutate(p_3b = case_when(pos=="3b" ~ 1, .default = 0)) %>% 
    mutate(p_ss = case_when(pos=="ss" ~ 1, .default = 0)) %>% 
    mutate(p_of = case_when(pos=="of" ~ 1, .default = 0)) %>% 
    mutate(p_ci = case_when(pos=="ci" ~ 1, .default = 0)) %>% 
    mutate(p_mi = case_when(pos=="mi" ~ 1, .default = 0)) %>% 
    mutate(p_dh = case_when(pos=="dh" ~ 1, .default = 0)) %>% 
    mutate(p_util = case_when(pos=="util" ~ 1, .default = 0)) %>% 
    mutate(p_p = case_when(pos=="p" ~ 1, .default = 0)) %>% 
    mutate(player = NA) %>% 
    mutate(row = row_number()) %>% 
    relocate(player, .after = pos)
  
  }

```

Function to load the player pool
```{r}

f_load_player_pool <- function() {
  
  #Create copy of the player pool for this simulation, including taken and available players
  simulation_player_pool <<- par
  
  rostered_players <<- simulation_player_pool %>% 
    filter(!is.na(billikenTeam)) %>% 
    #mutate(p_util = case_when(PA > 0 ~ 1, .default = 0)) %>% 
    mutate(p_p = case_when(IP > 0 ~ 1, .default = 0)) 
  
  #order by single position players first
  
  rostered_players_pos_pivot <<- 
    rostered_players %>%
      pivot_longer(
        cols = starts_with("p_"),
        names_to = "pos",
        names_prefix = "p_",
        values_to = "eligible",
        values_drop_na = TRUE
      ) %>% 
      filter(eligible == 1) %>% 
      filter(is.na(IP) | pos == "p")
  
  }

```


Function to fill rosters with keepers and drafted players
```{r}
f_fill_rosters_w_taken_players <- function() {
  
  #add logic to assign single position players first? 
  
  for (i in 1:nrow(rostered_players)) {
  #for (i in 1:120) {
  
  #i <- 121
  #print(i)
  
  #Name
  v_player <- rostered_players$Name[i]
  #v_player <- "Isiah Kiner-Falefa"
  #team
  v_team <- rostered_players$billikenTeam[i]
  #v_team <- "Free Birds"
  
  #print(v_player)
  #print(v_team)
  
  #check open positions on team
  open_positions <<- team_position_tibble %>% 
    filter(team == v_team) %>% 
    #filter(team == "Blue Socks") %>% 
    filter(is.na(player))  
  
  #assign position
  v_row <- pull(rostered_players_pos_pivot %>% 
                  filter(Name == v_player) %>% #positions this player can play
                  inner_join(replacement_level, join_by(pos)) %>% 
                  inner_join(open_positions, join_by(pos)) %>% 
                  arrange(repl_level) %>% 
                  slice(1) %>% 
                  select(row)
                )

  #could add logic to put a player on the bench if doesn't fit in current configuration
  
  v_row <- ifelse(length(v_row)==0,0,v_row)
  
  #print(v_row)
  
  #write player into position
  team_position_tibble <<- team_position_tibble %>% 
    mutate(player = ifelse(row == v_row,v_player,player))
    }
  
#team_position_tibble %>% 
#  arrange(player)

}
  
```


Start a single simulation of the draft

Start a single simulated pick

Function to create available players list
```{r}
f_reset_available_players <- function() {
  
  #create available players list
  available_players <<- simulation_player_pool %>% 
    filter(is.na(billikenTeam)) %>% 
    mutate(p_p = case_when(IP > 0 ~ 1, .default = 0))
    
  #pivot to one row per available position
  available_players_pos_pivot <<- available_players %>%
    pivot_longer(
      cols = starts_with("p_"),
      names_to = "pos",
      names_prefix = "p_",
      values_to = "eligible",
      values_drop_na = TRUE
    ) %>% 
    filter(eligible == 1) %>% 
    filter(is.na(IP) | pos == "p")
  
}
  
```


Function to load the draft order
```{r}

f_load_draft_order <- function() {
  
  draft_order <<- draft %>%
    rename(player = "Player...1", billikenTeam = Team, salary = Salary) %>% 
    mutate(contract = 1, salary = salary %>% as.numeric) %>% 
    filter(is.na(player) & !is.na(billikenTeam)) %>% 
    select(player, Round, Pick, billikenTeam, Owner)
  }

```

Function to identify the team that's on the clock for the next pick
```{r}
f_next_pick <- function() {
  
  next_pick <- draft_order %>% 
                     arrange(Round, Pick)  %>% 
                     filter(is.na(player)) %>% 
                     slice(1) %>%
                     select(Round, Pick, billikenTeam)
  
  v_round <<- pull(next_pick %>% 
                     select(Round)
                   )
  
  v_pick <<- pull(next_pick %>% 
                     select(Pick)
                   )
  
  v_team_on_clock <<- pull(next_pick %>% 
                     select(billikenTeam)
                   )
  
  }

```


next eligible players for remaining roster spots
```{r}
f_make_next_pick <- function() {
  
  f_reset_available_players()
  
  #identify the team, round, and pick up next
  f_next_pick()
  #v_team_on_clock <- "Blue Socks"
  #v_round = 
  #v_pick = 

  #check if roster is full
    #if so, end

  #determine open roster spots
  open_positions <<- team_position_tibble %>% 
    filter(team == v_team_on_clock) %>% 
    filter(is.na(player)) 

  #distinct eligible players to be selected
  eligible_players <<- available_players_pos_pivot %>% 
    inner_join(open_positions, join_by(pos)) %>% 
    arrange(desc(ev)) %>% 
    distinct(Name, .keep_all = TRUE) 
  
  #check salary cap for eligibility

  #stop the pick if no eligible players/spots left
  
  if (nrow(eligible_players) > 0) {
      
    #add some randomness to the draft
    eligible_players$rand <- rnorm(nrow(eligible_players), mean = 0, sd = 2)
    
    #add smarter picks for Blue Socks, other teams? 
    
    #make pick
    v_player <<- pull(eligible_players %>% 
      mutate(rand_ev = ev + rand) %>% 
      arrange(desc(rand_ev)) %>% 
      slice(1) %>% 
      select(Name))
    
    #assign position to selected player
    v_row <- pull(available_players_pos_pivot %>% 
                    filter(Name == v_player) %>% #positions this player can play
                    inner_join(replacement_level, join_by(pos)) %>% 
                    inner_join(open_positions, join_by(pos)) %>% 
                    arrange(repl_level) %>% 
                    slice(1) %>% 
                    select(row)
                  )
    
    #print(v_row)
    
    #write player into position
    team_position_tibble <<- 
      team_position_tibble %>% 
        mutate(player = ifelse(row == v_row, v_player, player))
    
    #update simulated rosters
    simulation_player_pool <<- simulation_player_pool %>% 
        mutate(billikenTeam = ifelse(Name == v_player, v_team_on_clock, billikenTeam))
    
    draft_order <<- draft_order %>% 
        mutate(player = ifelse(Round == v_round & Pick == v_pick, v_player, player))
    
    
  } else {

    draft_order <<- draft_order %>% 
        mutate(player = ifelse(Round == v_round & Pick == v_pick, "pass", player))
    
  }
  
  
}

#simulation_player_pool
#team_position_tibble
  
```


Test making one pick
```{r}

#set up draft simulation
f_create_empty_rosters() 
f_load_player_pool()
f_fill_rosters_w_taken_players()
f_load_draft_order()

#identify next team to pick for test
#(called automatically in f_make_next_pick later)
f_next_pick()

simulation_player_pool %>% 
  filter(billikenTeam == v_team_on_clock) %>% 
  arrange(desc(contract))

team_position_tibble %>% 
  filter(team == v_team_on_clock)

f_make_next_pick()
  
simulation_player_pool %>% 
  filter(billikenTeam == v_team_on_clock) %>% 
  arrange(desc(contract))

team_position_tibble %>% 
  filter(team == v_team_on_clock)


```


Function to run 1 simulated draft
```{r}

f_simulate_draft <- function() {
  
  f_create_empty_rosters() 
  f_load_player_pool()
  f_fill_rosters_w_taken_players()
  f_load_draft_order()

  for (i in 1:nrow(draft_order)) {
  #for (i in 1:10) {
  
    f_make_next_pick()
  }
  
}


#evaluate draft

#add up team totals


#record results 
#simulation_num, team_totals

```

Run 1 simulated draft
```{r}

f_load_draft_order()
draft_order

f_simulate_draft()

draft_order

simulation_player_pool

team_position_tibble

f_calculate_standings()

simulated_standings

```

Calculate simulated standings
```{r}


f_calculate_standings <- function(i = 1) {

#summarize results

simulated_team_totals <- simulation_player_pool %>% 
  filter(!is.na(billikenTeam)) %>% 
  group_by(billikenTeam) %>% 
  #summarize(salary = sum(salary), point_value, par, ev, surplus)
  summarise(n=n(), across(c("salary","point_value","par","ev","surplus"), ~ sum(.x, na.rm = TRUE)), PA = sum(PA, na.rm=TRUE), AB = sum(AB, na.rm=TRUE), H = sum(H, na.rm=TRUE), HR = sum(HR, na.rm=TRUE), R = sum(R, na.rm=TRUE), RBI = sum(RBI, na.rm=TRUE), SB = sum(SB, na.rm=TRUE), AVG = sum(H, na.rm=TRUE)*1.0/sum(AB, na.rm=TRUE), W = sum(W, na.rm=TRUE), SV = sum(SV, na.rm=TRUE), IP = sum(IP, na.rm=TRUE), SO = sum(SO, na.rm=TRUE), ER = sum(ER, na.rm=TRUE), ERA = sum(ER, na.rm=TRUE)*9/sum(IP, na.rm=TRUE), WHIP = (sum(WH, na.rm=TRUE))/sum(IP, na.rm=TRUE)) 

simulation_standings <- simulated_team_totals %>% 
  mutate(hr = n_teams+1 - dense_rank(desc(HR)), r = n_teams+1 - dense_rank(desc(R)), rbi = n_teams+1 - dense_rank(desc(RBI)), sb = n_teams+1 - dense_rank(desc(SB)), avg = n_teams+1 - dense_rank(desc(AVG))) %>% 
  mutate(w = n_teams+1 - dense_rank(desc(W)), sv = n_teams+1 - dense_rank(desc(SV)), so = n_teams+1 - dense_rank(desc(SO)), era = n_teams+1 - dense_rank(ERA), whip = n_teams+1 - dense_rank(WHIP)) %>%
  mutate(hit = hr + r + rbi + sb + avg) %>% 
  mutate(pit = w + sv + so + era + whip) %>% 
  mutate(total_points = hit + pit) %>% 
  mutate(total_points_rank = dense_rank(desc(total_points))) %>% 
  mutate(sim_num = i) %>% 
  relocate(sim_num, .before = billikenTeam) %>% 
  arrange(desc(total_points_rank))


 if (i == 1) {
   simulated_standings <<- simulation_standings
 } else {
   simulated_standings <<- bind_rows(simulated_standings,simulation_standings)
 }

}


```


Function to simulate multiple drafts
```{r}

  for (i in 1:100) {

    print(paste("Starting simulation #",i))
    
  suppressWarnings({ 
    
    f_load_draft_order()
    
    f_simulate_draft()
    
    f_calculate_standings(i)
    
    })

  }

simulated_standings %>% 
  group_by(billikenTeam) %>% 
  summarize(n = n(), wins = sum(case_when(total_points_rank==1 ~ 1, .default = 0) ), across(everything(), mean)) %>% 
  arrange(total_points_rank)

```


